Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-12 eswc-2012/phdsymp.tex
abstract
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@74 43ef1190-90fd-4dd7-a769-d0121f02b80e

\begin{abstract}

\end{abstract}

@@

\section{Conclusion}

>>>>

\begin{abstract}
Federation of semantic data on SPARQL endpoints will allow data to
remain distributed so that they can be controlled by local curators
and swiftly updated. It creates considerable performance problems,
however, that is intended in the suggested work to be addressed mainly
by computation and exposure of statistical digests to assist
selectivity estimation.

Discontent with current state of the art in benchmarking prompts the
author to devote much of the time to the evaluation problem and to
challenge the notion that a ``one-size-fits-all'' benchmark is
impossible.
\end{abstract}

@@

%\section{Conclusion}
